---
title: "Rmarkdown for Assignement 1"
author: "Aaron Nematnejad"
date: "Sunday, January 18, 2015"
output: html_document
---
The first thing that we need to do for this assignement is to take the "activity.csv" file and save it in a folder on the desktop which takes the directory in the following form:  
Desktop/Coursera/Reprod.

Now we read the file into R.

```{r}
a<-read.csv("activity.csv",header= TRUE)
b<-na.omit(a)
print(head(b))



```

Now sum the number of steps on each interval
```{r}
d<-aggregate(steps~date, data=b, FUN=sum)

```

What is mean total number of steps taken per day?

```{r, echo=FALSE}
with(d, hist(d$steps, main="Number of Steps", col="red", ylab="Steps/day",  xlab = "Count"))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


What is mean and median of the total number of steps taken per day?

```{r}
mean(d$steps)

```
and mendian number of steps:-

```{r}
median(d$steps)
```

Average Daily Activity Pattern

```{r}
e<-aggregate(steps~interval, data=b, FUN=mean)

```



plot of the data 


```{r, echo=FALSE}
plot(e$interval, e$steps, type ="l", xlab="5 min Interval", ylab="Avg Steps")

```

to get the interval with the max amount of steps, we first calculate the max number of steps:- 

```{r}
max(e$steps)

```

and the interval in which this is accomplished is:-

```{r}
subset(e$interval, e$steps==max(e$steps))

```

Calculating number of rows with missing values

```{r}
nrow(is.na(a))
```

Total Number of Rows:  
```{r}
nrow((a))
```

Number of completed rows without NA

is difference between 2 numbers.
